Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-15 paper/sheaf_lics.tex
more detailed comment on section 4

\nt{Il faut introduire c'est propriété, $\Type_n^\modal$ is a sheaf
  est très importante en particulier. Il faut qu'on comprenne d'où ça
  vient et que tu fasses un preuve, même un peu idalisée}

From these definitions, one can show that
\begin{prop}\label{prop:sheaf_prop}
  \begin{itemize}
  \item $\Type_n^\modal$ is a sheaf.
  \item If $A:\Type_{n+1}$ and $B:A \to \Type_{n+1}$ such that for any
    $a:A$, $(B~a)$ is a sheaf, then $\prod_{a:A}B~a$ is a sheaf.
  \end{itemize}
\end{prop}

@@

\begin{proof}
We will use the following lemma~:
\begin{lem}
  A $(n+1)$-truncated type $T$ with an embedding $f : T \to U$
  into a separated $(n+1)$-truncated type $U$ is itself separated.
\end{lem}
As $\square T$ embeds in $\left( \Type_n^\modal \right)^T$, we only
have to show that the latter is separated. But it is the case with
both parts proposition~\ref{prop:sheaf_prop}.
\end{proof}

>>>>

\nt{Il faut introduire c'est propriété, $\Type_n^\modal$ is a sheaf
  est très importante en particulier. Il faut qu'on comprenne d'où ça
  vient et que tu fasses une preuve, même un peu idalisée. Je dirais
  que tu peux mettre des lemmes genres nj\_inter en disant que telle
  flèche est un iso, and co.
  En tout cas, cette partie peut et doit être bien plus longue.
}

\begin{prop}\label{prop:sheaf-forall}
  If $A:\Type_{n+1}$ and $B:A \to \Type_{n+1}$ such that for any
  $a:A$, $(B~a)$ is a sheaf, then $\prod_{a:A}B~a$ is a sheaf.
\end{prop}

\begin{prop}\label{prop:sheaf-is-sheaf}
  $\Type_n^\modal$ is a sheaf.
\end{prop}

@@

\begin{proof}
We will use the following lemma~:
\begin{lem}
  A $(n+1)$-truncated type $T$ with an embedding $f : T \to U$
  into a separated $(n+1)$-truncated type $U$ is itself separated.
\end{lem}
As $\square T$ embeds in $\left( \Type_n^\modal \right)^T$, we only
have to show that the latter is separated. But it is the case because
$\Type_n^\modal$ is a sheaf (by Proposition~\ref{prop:sheaf-is-sheaf})
and a function type is a sheaf as soon
as its codomain is a sheaf (by Proposition~\ref{prop:sheaf-forall}).
\end{proof}
